Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-04 robdml.tex
svg
tex

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the security implications of adversarial vulnerability, the
	adversarial robustness of deep metric learning models has to be improved
	via defense.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing defenses refrain from using the min-max adversarial training, but
	instead learns from a weak adversary inefficiently.
	% our starting point
	Conversely, we argue that a model can learn from a strong adversary without
	collapse, where the key is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb the
	training triplet to increase its hardness into a specified level, according
	to another benign triplet or a pseudo-hardness function.
	% GA Adversary
	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
	functions to overcome problems of referencing other benign triplets, and
	achieve a better balance in the learning objective.
	% Intra-Class Structure
	Besides, a penalty on Intra-Class Structure among benign and adversarial
	examples can further improve model robustness, which is neglected by
	previous methods.
	% Experiment and Conclusion
	Comprehensive experimental results on commonly used deep metric
	learning datasets suggest that the proposed method, although simple in
	its form, overwhelmingly outperforms the state-of-the-art defense methods in
	terms of training time cost, robustness, as well as recall performance on
	benign examples.
%
\end{abstract}

@@

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to security implications of adversarial vulnerability, adversarial
	robustness of deep metric learning models has to be improved.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing defenses dismiss the min-max adversarial training, but instead
	learn from a weak adversary inefficiently.
	% our starting point
	Conversely, we propose Hardness Manipulation to efficiently perturb the
	training triplet till a specified level of hardness for adversarial
	training, according to a harder benign triplet or a pseudo-hardness
	function.
	% merit
	It is flexible as regular training and min-max adversarial training
	are its boundary cases.
	% GA Adversary
	Besides, Gradual Adversary, a family of pseudo-hardness functions is
	proposed to gradually increase the specified hardness level during training
	for a better balance between performance and robustness.
	% Intra-Class Structure
	Additionally, an Intra-Class Structure loss term among benign and adversarial
	examples further improves training efficiency and model robustness.
	% Experiment and Conclusion
	Comprehensive experimental results suggest that the proposed method,
	although simple in its form, overwhelmingly outperforms the
	state-of-the-art defenses in terms of training cost,
	robustness, as well as performance on benign examples.
%
\end{abstract}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{hmflexible.pdf}
	\vspace{-1.8em}
	\caption{Flexibility of Hardness Manipulation.
	%
	Regular training and min-max adversarial training are two of its boundary cases.
	}
	\label{fig:hmflexible}
\end{figure}
